Price of Anarchy for Mean Field Games

### 2018-07-04 PoA.tex
small typos

This is a linear FBSDE of McKean-Vlasov type, which can be solved explicitly under mild assumptions (or at least in the case of time-independent coefficients which we will consider later. See Appendix \ref{appendix_solving_fbsdes}). Let $\bar{\eta}_t^{MFG}$, $\eta_t^{MFG}$, $\bar{x}_t^{MFG}$, and $v^{MFG}_t$ denote the solutions for this problem as described in the appendix so that $Y_t=\eta_t^{MFG}X_t+(\bar{\eta}_t^{MFG}-\eta_t^{MFG})\bar{x}_t^{MFG}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MFG}\bar{x}_t^{MFG}$, $\mathbb{E}(X_t)=\bar{x}_t^{MFG}$, and $Var(X_t)=v^{MFG}_t$ provide a solution to the LQEMFG problem. Then from the appendix, we have:
\begin{equation}
\begin{split}
\dot{\bar{\eta}}^{MFG}_t+c^{MFG}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MFG}_t)^2+(2b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MFG}_t +q(t)+\bar{q}(t)(1-s(t))&=0,\\
\bar{\eta}^{MFG}_T-(q_T+\bar{q}_T(1-s_T))&=0,
\end{split}
\label{eq:eta_bar_MFG}
\end{equation}
\begin{equation}
\begin{split}
\dot{\eta}^{MFG}_t+a^{MFG}(t)b_2(t)(\eta^{MFG}_t)^2+2b_1(t)\eta^{MFG}_t+q(t)+\bar{q}(t)&=0, \\
\eta^{MFG}_T-(q_T+\bar{q}_T)&=0,
\end{split}
\end{equation}
\begin{equation}
\begin{split}
\dot{\bar{x}}^{MFG}_t&=(b_1(t)+\bar{b}_1(t)+c^{MFG}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MFG}_t)\bar{x}^{MFG}_t, \\
\bar{x}^{MFG}_0&=\mathbb{E}(\xi).
\end{split}
\label{eq:x_bar_MFG}
\end{equation}
And thus,
\begin{equation}
\bar{x}^{MFG}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MFG}(u)(b_2(u)+\bar{b}_2(u))\bar{\eta}^{MFG}_u)du},
\label{eq:x_bar_MFG_explicit}
\end{equation}
\begin{equation}
v_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MFG}(s)b_2(s)\eta^{MFG}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MFG}(u)b_2(u)\eta^{MFG}_u) du}ds.
\label{eq:v_t}
\end{equation}
Let $SC^{MFG}:=SC(\phi)$ for the feedback function specified by this solution, i.e.
\begin{equation*}
    \phi(t,x)=a^{MFG}(t)\eta_t^{MFG}x+\left(a^{MFG}(t)(\bar{\eta}_t^{MFG}-\eta_t^{MFG})+b^{MFG}(t)\bar{\eta}_t^{MFG} \right)\bar{x}_t^{MFG}.
\end{equation*}
Then we can compute the social cost as described in Section \ref{sub:MFG_formulation}:
\begin{equation*}
\begin{split}
    SC^{MFG}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MFG}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2\\
    &+\int_0^T (q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MFG}(t)\eta_t^{MFG})^2)v_t^{MFG}\\
    &+(q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MFG}(t)\bar{\eta}_t^{MFG})^2)(\bar{x}_t^{MFG})^2dt],
\end{split}
\end{equation*}
where we have used the fact that:
\begin{equation*}
    \mathbb{E}(\phi(t,X_t))=c^{MFG}(t)\bar{\eta}_t^{MFG}\bar{x}_t^{MFG},
\end{equation*}
and:
\begin{equation*}
    Var(\phi(t,X_t))=(a^{MFG}(t)\eta_t^{MFG})^2v^{MFG}_t.
\end{equation*}

@@

As in the previous section, this is a linear FBSDE of McKean-Vlasov type, which can be solved explicitly under mild assumptions (or at least in the case of time-independent coefficients which we will consider later. See Appendix \ref{appendix_solving_fbsdes}). Let $\bar{\eta}_t^{MKV}$, $\eta_t^{MKV}$, $\bar{x}_t^{MKV}$, and $v^{MKV}_t$ so that $Y_t=\eta_t^{MKV}X_t+(\bar{\eta}_t^{MKV}-\eta_t^{MKV})\bar{x}_t^{MKV}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}$, $\mathbb{E}(X_t)=\bar{x}_t^{MKV}$, and $Var(X_t)=v^{MKV}_t$ provide a solution to the LQEMKV problem. Then from the appendix, we have:
\begin{equation}
\begin{split}
\dot{\bar{\eta}}^{MKV}_t+c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MKV}_t)^2+2(b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MKV}_t +q(t)+\bar{q}(t)(1-s(t))^2&=0,\\
\bar{\eta}^{MKV}_T-(q_T+\bar{q}_T(1-s_T)^2)&=0,
\end{split}
\label{eq:eta_bar_MKV}
\end{equation}
\begin{equation}
\begin{split}
\dot{\eta}^{MKV}_t+a^{MKV}(t)b_2(t)(\eta^{MKV}_t)^2+2b_1(t)\eta^{MKV}_t+q(t)+\bar{q}(t)&=0, \\
\eta^{MKV}_T-(q_T+\bar{q}_T)&=0,
\end{split}
\end{equation}
\begin{equation}
\begin{split}
\dot{\bar{x}}^{MKV}_t&=(b_1(t)+\bar{b}_1(t)+c^{MKV}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MKV}_t)\bar{x}^{MKV}_t, \\
\bar{x}^{MKV}_0&=\mathbb{E}(\xi).
\end{split}
\label{eq:x_bar_MKV}
\end{equation}
And thus,
\begin{equation*}
\bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MKV}(u)(b_2(u)+\bar{b}_2(u)\bar{\eta}^{MKV}_u)du},
\end{equation*}
\begin{equation*}
v_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u) du}ds.
\end{equation*}
Then $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, i.e.
\begin{equation*}
    \phi(t,x)=a^{MKV}(t)\eta_t^{MKV}x+\left(a^{MKV}(t)(\bar{\eta}_t^{MKV}-\eta_t^{MKV})+b^{MKV}(t)\bar{\eta}_t^{MKV} \right)\bar{x}_t^{MKV}.
\end{equation*}
Then we can compute the social cost, denoted $SC^{MKV}$, as described in Section \ref{sub:MKV_formulation}:
\begin{equation*}
\begin{split}
    SC^{MKV}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MKV}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MKV})^2\\
    &+\int_0^T (q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MKV}(t)\eta_t^{MKV})^2)v_t^{MKV}dt \\
    &+\int_0^T(q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2)(\bar{x}_t^{MKV})^2dt],
\end{split}
\end{equation*}
where we have used the fact that:
\begin{equation*}
    \mathbb{E}(\phi(t,X_t))=c^{MKV}(t)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV},
\end{equation*}
and:
\begin{equation*}
    Var(\phi(t,X_t))=(a^{MKV}(t)\eta_t^{MKV})^2v^{MKV}_t.
\end{equation*}

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}),
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad and \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	When assumption $(\ref{eq:assumptions})$ is satisfied, we have the existence and uniqueness of solutions for the scalar Riccati equations associated with $u_t$, $w_t$ and $\eta_t$.

	When $r \to \infty$ we have
	\begin{equation*}
		\lambda \to \lambda^{\infty,r} := \frac{b_2}{b_2 + \bar{b}_2}
	\end{equation*}
	and
	\begin{equation*}
		B \to 0,\ B^\eta \to 0,\ C^u \to C_u^{\infty,r} := \lambda^{\infty,r}(q + \bar{q}(1-s)),\ D^{u} \to D_u^{\infty,r} := \lambda^{\infty,r}(q_T+ \bar{q}_T(1-s_T)).
	\end{equation*}
	Since assumption (\ref{eq:assumptions}) holds for arbitrary large $r$, we can deduce that the solution $u_t$ of equation (\ref{eq:riccati_ut}) tends to a limiting function $u^{\infty,r}_t$ which is the solution of a first-order differential equation (see Appendix \ref{appendix_solving_fbsdes}). The limiting solution $u_t^{\infty,r}$ is given by:
	\begin{equation*}
	\begin{split}
	    \text{when } A^u \neq 0,\qquad & u_t^{\infty,r} = \left(D^{\infty,r}_u - \frac{C^{\infty,r}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{\infty,r}_u}{2A^u}\\
	    \text{when } A^u = 0, \qquad & u_t^{\infty,r} = D^{\infty,r}_u + C^{\infty,r}_u (T-t)
	\end{split}
	\end{equation*}
	which is bounded for $t \in [0,T]$.
	Similarly, we have the bounded limiting solutions over $[0,T]$:
	$$w_t \xrightarrow[r \to \infty]{} w_t^{\infty,r},\qquad \eta_t \xrightarrow[r \to \infty]{} \eta_t^{\infty,r}.$$
	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, we have 
	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \bar{x}_0 e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
	  v_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{\infty,r}_t
	$$
	which are also bounded over $t\in[0,T]$.
	Hence, by the bounded convergence theorem we have
	\begin{equation*}
		\lim_{r \to \infty} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = \int_0^T (u^{\infty,r}_t- w^{\infty,r}_t)^2 (\bar{x}_t^{\infty,r,MFG})^2 dt \  < \infty.
	\end{equation*}
	By their explicit formulas, it can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_0 >0$ for $t>0$ and therefore,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV} = \int_0^T (q+\bar{q}) v^{\infty,r}_t dt + (q_T + \bar{q}_T) v^{\infty,r}_T + w^{\infty,r}_0 \bar{x}_0^2 \  >0.
	\end{equation*}
	Thus, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we deduce $\displaystyle \lim_{r \to \infty} PoA = 1$.

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1\neq 0$, then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{0,\bar{b}_2} > 1\qquad and \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	For the case $\bar{b}_2 \to 0$, we have $\displaystyle \lambda \to \lambda^{0,\bar{b}_2} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}$
	and 
	$$B \to B^{0,\bar{b}_2} := \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} \neq 0,\ C^u \to C^{0,\bar{b}_2}_u >0 ,\ D^u \to D^{0,\bar{b}_2}_u \geq 0.$$
	Thus, the existence and uniqueness for solutions of the Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}) associated with $u_t$ and $w_t$, respectively, in the limiting region $\bar{b}_2 \to 0$ still hold. Let's denote the limiting solutions by 
	$u^{0,\bar{b}_2}_t, w^{0,\bar{b}_2}_t$. By the bounded convergence theorem, the mean function $\bar{x}_t^{MFG}$ has the limit:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG} = \bar{x}_0 e^{\int_0^t (b_1 + \bar{b}_1 - B^{0,\bar{b}_2}\cdot u^{0,\bar{b}_2}_t) dt} =: \bar{x}^{0,\bar{b}_2,MFG}_t.$$ 
   	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{0,\bar{b}_2}_t\neq w^{0,\bar{b}_2}_t$ on a set of positive Lebesgue measure.
   	Thus, by the bounded convergence theorem and the assumption on $\xi$, we deduce
	$$ \lim_{\bar{b}_2 \to 0} \Delta SC = \frac{1}{2} B^{0,\bar{b}_2} \int_0^T \left( (u_t^{0,\bar{b}_2} - w_t^{0,\bar{b}_2})\cdot \bar{x}_t^{0,\bar{b}_2,MFG} \right)^2 dt \  > 0. $$
	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. By the explicit formula, $0<v_t<\infty$ for $t>0$ and $0 \leq w^{0,\bar{b}_2}_0 < \infty$, and thus,
	\begin{equation*}
    \begin{split}
	    \lim_{\bar{b}_2 \to 0}SC^{MKV} &= h_{var} + w^{0,\bar{b}_2}_0 \bar{x}_0^2, \\
	    \lim_{\bar{b}_2 \to 0}SC^{MKV}&<\infty, \\
	    \lim_{\bar{b}_2 \to 0}SC^{MKV}&>0 .       
    \end{split}
	\end{equation*}
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA =: PoA^{0,\bar{b}_2} > 1. $$

>>>>

This is a linear FBSDE of McKean-Vlasov type, which can be solved explicitly under mild assumptions (or at least in the case of time-independent coefficients which we will consider later. See Appendix \ref{appendix_solving_fbsdes}). Let $\bar{\eta}_t^{MFG}$, $\eta_t^{MFG}$, $\bar{x}_t^{MFG}$, and $v^{MFG}_t$ denote the solutions for this problem as described in the appendix so that $Y_t=\eta_t^{MFG}X_t+(\bar{\eta}_t^{MFG}-\eta_t^{MFG})\bar{x}_t^{MFG}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MFG}\bar{x}_t^{MFG}$, $\mathbb{E}(X_t)=\bar{x}_t^{MFG}$, and $Var(X_t)=v^{MFG}_t$ provide a solution to the LQEMFG problem. Then from the appendix, we have:
\begin{equation}
\begin{split}
\dot{\bar{\eta}}^{MFG}_t+c^{MFG}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MFG}_t)^2+(2b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MFG}_t +q(t)+\bar{q}(t)(1-s(t))&=0,\\
\bar{\eta}^{MFG}_T-(q_T+\bar{q}_T(1-s_T))&=0,
\end{split}
\label{eq:eta_bar_MFG}
\end{equation}
\begin{equation}
\begin{split}
\dot{\eta}^{MFG}_t+a^{MFG}(t)b_2(t)(\eta^{MFG}_t)^2+2b_1(t)\eta^{MFG}_t+q(t)+\bar{q}(t)&=0, \\
\eta^{MFG}_T-(q_T+\bar{q}_T)&=0,
\end{split}
\end{equation}
\begin{equation}
\begin{split}
\dot{\bar{x}}^{MFG}_t&=(b_1(t)+\bar{b}_1(t)+c^{MFG}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MFG}_t)\bar{x}^{MFG}_t, \\
\bar{x}^{MFG}_0&=\mathbb{E}(\xi).
\end{split}
\label{eq:x_bar_MFG}
\end{equation}
And thus,
\begin{equation}
\bar{x}^{MFG}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MFG}(u)(b_2(u)+\bar{b}_2(u))\bar{\eta}^{MFG}_u)du},
\label{eq:x_bar_MFG_explicit}
\end{equation}
\begin{equation}
v^{MFG}_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MFG}(s)b_2(s)\eta^{MFG}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MFG}(u)b_2(u)\eta^{MFG}_u) du}ds.
\label{eq:v_t}
\end{equation}
Let $SC^{MFG}:=SC(\phi)$ for the feedback function specified by this solution, i.e.
\begin{equation*}
    \phi(t,x)=a^{MFG}(t)\eta_t^{MFG}x+\left(a^{MFG}(t)(\bar{\eta}_t^{MFG}-\eta_t^{MFG})+b^{MFG}(t)\bar{\eta}_t^{MFG} \right)\bar{x}_t^{MFG}.
\end{equation*}
Then we can compute the social cost as described in Section \ref{sub:MFG_formulation}:
\begin{equation*}
\begin{split}
    SC^{MFG}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MFG}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2\\
    &+\int_0^T (q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MFG}(t)\eta_t^{MFG})^2)v_t^{MFG}\\
    &+(q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MFG}(t)\bar{\eta}_t^{MFG})^2)(\bar{x}_t^{MFG})^2dt],
\end{split}
\end{equation*}
where we have used the fact that:
\begin{equation*}
    \mathbb{E}(\phi(t,X_t))=c^{MFG}(t)\bar{\eta}_t^{MFG}\bar{x}_t^{MFG},
\end{equation*}
and:
\begin{equation*}
    Var(\phi(t,X_t))=(a^{MFG}(t)\eta_t^{MFG})^2v^{MFG}_t.
\end{equation*}

@@

As in the previous section, this is a linear FBSDE of McKean-Vlasov type, which can be solved explicitly under mild assumptions (or at least in the case of time-independent coefficients which we will consider later. See Appendix \ref{appendix_solving_fbsdes}). Let $\bar{\eta}_t^{MKV}$, $\eta_t^{MKV}$, $\bar{x}_t^{MKV}$, and $v^{MKV}_t$ so that $Y_t=\eta_t^{MKV}X_t+(\bar{\eta}_t^{MKV}-\eta_t^{MKV})\bar{x}_t^{MKV}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}$, $\mathbb{E}(X_t)=\bar{x}_t^{MKV}$, and $Var(X_t)=v^{MKV}_t$ provide a solution to the LQEMKV problem. Then from the appendix, we have:
\begin{equation}
\begin{split}
\dot{\bar{\eta}}^{MKV}_t+c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MKV}_t)^2+2(b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MKV}_t +q(t)+\bar{q}(t)(1-s(t))^2&=0,\\
\bar{\eta}^{MKV}_T-(q_T+\bar{q}_T(1-s_T)^2)&=0,
\end{split}
\label{eq:eta_bar_MKV}
\end{equation}
\begin{equation}
\begin{split}
\dot{\eta}^{MKV}_t+a^{MKV}(t)b_2(t)(\eta^{MKV}_t)^2+2b_1(t)\eta^{MKV}_t+q(t)+\bar{q}(t)&=0, \\
\eta^{MKV}_T-(q_T+\bar{q}_T)&=0,
\end{split}
\end{equation}
\begin{equation}
\begin{split}
\dot{\bar{x}}^{MKV}_t&=(b_1(t)+\bar{b}_1(t)+c^{MKV}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MKV}_t)\bar{x}^{MKV}_t, \\
\bar{x}^{MKV}_0&=\mathbb{E}(\xi).
\end{split}
\label{eq:x_bar_MKV}
\end{equation}
And thus,
\begin{equation*}
\bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MKV}(u)(b_2(u)+\bar{b}_2(u)\bar{\eta}^{MKV}_u)du},
\end{equation*}
\begin{equation*}
v^{MKV}_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u) du}ds.
\end{equation*}
Then $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, i.e.
\begin{equation*}
    \phi(t,x)=a^{MKV}(t)\eta_t^{MKV}x+\left(a^{MKV}(t)(\bar{\eta}_t^{MKV}-\eta_t^{MKV})+b^{MKV}(t)\bar{\eta}_t^{MKV} \right)\bar{x}_t^{MKV}.
\end{equation*}
Then we can compute the social cost, denoted $SC^{MKV}$, as described in Section \ref{sub:MKV_formulation}:
\begin{equation*}
\begin{split}
    SC^{MKV}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MKV}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MKV})^2\\
    &+\int_0^T (q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MKV}(t)\eta_t^{MKV})^2)v_t^{MKV}dt \\
    &+\int_0^T(q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2)(\bar{x}_t^{MKV})^2dt],
\end{split}
\end{equation*}
where we have used the fact that:
\begin{equation*}
    \mathbb{E}(\phi(t,X_t))=c^{MKV}(t)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV},
\end{equation*}
and:
\begin{equation*}
    Var(\phi(t,X_t))=(a^{MKV}(t)\eta_t^{MKV})^2v^{MKV}_t.
\end{equation*}

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}),
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	When assumption $(\ref{eq:assumptions})$ is satisfied, we have the existence and uniqueness of solutions for the scalar Riccati equations associated with $u_t$, $w_t$ and $\eta_t$.

	When $r \to \infty$ we have
	\begin{equation*}
		\lambda \to \lambda^{\infty,r} := \frac{b_2}{b_2 + \bar{b}_2}
	\end{equation*}
	and
	\begin{equation*}
		B \to 0,\ B^\eta \to 0,\ C^u \to C_u^{\infty,r} := \lambda^{\infty,r}(q + \bar{q}(1-s)),\ D^{u} \to D_u^{\infty,r} := \lambda^{\infty,r}(q_T+ \bar{q}_T(1-s_T)).
	\end{equation*}
	Since assumption (\ref{eq:assumptions}) holds for arbitrary large $r$, we can deduce that the solution $u_t$ of equation (\ref{eq:riccati_ut}) tends to a limiting function $u^{\infty,r}_t$ which is the solution of a first-order differential equation (see Appendix \ref{appendix_solving_fbsdes}). The limiting solution $u_t^{\infty,r}$ is given by:
	\begin{equation*}
	\begin{split}
	    \text{when } A^u \neq 0,\qquad & u_t^{\infty,r} = \left(D^{\infty,r}_u - \frac{C^{\infty,r}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{\infty,r}_u}{2A^u},\\
	    \text{when } A^u = 0, \qquad & u_t^{\infty,r} = D^{\infty,r}_u + C^{\infty,r}_u (T-t),
	\end{split}
	\end{equation*}
	which is bounded for $t \in [0,T]$.
	Similarly, we have the bounded limiting solutions over $[0,T]$:
	$$w_t \xrightarrow[r \to \infty]{} w_t^{\infty,r},\qquad \eta_t \xrightarrow[r \to \infty]{} \eta_t^{\infty,r}.$$
	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, we have 
	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
	  v_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{\infty,r}_t
	$$
	which are also bounded over $t\in[0,T]$.
	Hence, by the bounded convergence theorem we have
	\begin{equation*}
		\lim_{r \to \infty} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = \int_0^T (u^{\infty,r}_t- w^{\infty,r}_t)^2 (\bar{x}_t^{\infty,r,MFG})^2 dt \  < \infty.
	\end{equation*}
	By their explicit formulas, it can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_t >0$ for $t>0$ and therefore,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV} = \int_0^T (q+\bar{q}) v^{\infty,r}_t dt + (q_T + \bar{q}_T) v^{\infty,r}_T + w^{\infty,r}_0 \bar{x}_0^2 \  >0.
	\end{equation*}
	Thus, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we deduce $\displaystyle \lim_{r \to \infty} PoA = 1$.

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1\neq 0$, then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{0,\bar{b}_2} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	For the case $\bar{b}_2 \to 0$, we have $\displaystyle \lambda \to \lambda^{0,\bar{b}_2} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}$
	and 
	$$B \to B^{0,\bar{b}_2} := \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} \neq 0,\ C^u \to C^{0,\bar{b}_2}_u >0 ,\ D^u \to D^{0,\bar{b}_2}_u \geq 0.$$
	Thus, the existence and uniqueness for solutions of the Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}) associated with $u_t$ and $w_t$, respectively, in the limiting region $\bar{b}_2 \to 0$ still hold. Let's denote the limiting solutions by 
	$u^{0,\bar{b}_2}_t, w^{0,\bar{b}_2}_t$. By the bounded convergence theorem, the mean function $\bar{x}_t^{MFG}$ has the limit:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG} = \bar{x}_0 e^{\int_0^t (b_1 + \bar{b}_1 - B^{0,\bar{b}_2}\cdot u^{0,\bar{b}_2}_t) dt} =: \bar{x}^{0,\bar{b}_2,MFG}_t.$$ 
   	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{0,\bar{b}_2}_t\neq w^{0,\bar{b}_2}_t$ on a set of positive Lebesgue measure.
   	Thus, by the bounded convergence theorem and the assumption on $\xi$, we deduce
	$$ \lim_{\bar{b}_2 \to 0} \Delta SC = \frac{1}{2} B^{0,\bar{b}_2} \int_0^T \left( (u_t^{0,\bar{b}_2} - w_t^{0,\bar{b}_2})\cdot \bar{x}_t^{0,\bar{b}_2,MFG} \right)^2 dt \  > 0. $$
	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. By the explicit formula, $0<v_t<\infty$ for $t>0$ and $0 \leq w^{0,\bar{b}_2}_0 < \infty$, and thus,
	\begin{equation*}
    \begin{split}
	    \lim_{\bar{b}_2 \to 0}SC^{MKV} &= h_{var} + w^{0,\bar{b}_2}_0 \bar{x}_0^2, \\
	    \lim_{\bar{b}_2 \to 0}SC^{MKV}&<\infty, \\
	    \lim_{\bar{b}_2 \to 0}SC^{MKV}&>0 .       
    \end{split}
	\end{equation*}
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA =: PoA^{0,\bar{b}_2} > 1. $$
